### 2015-08-05 thesis/language-overview.tex
revised abstract

% !TEX root = omar-thesis.tex
\chapter{Language Overview}\label{chap:language-overview}
\todo{integrate this point}
An important observation is that dialects that have substantially different type structure are still often implemented by translation to a simple and stable intermediate language. For example, the Glasgow Haskell Compiler's intermediate language has remained stable for many years, even as the number of Haskell dialects that the compiler supports has grown. Similarly, the primary Scala compiler uses the Java virtual machine (JVM) bytecode language as an intermediate language, which has also evolved relatively slowly.
\section{External Language}\label{sec:EL-overview}
\section{Internal Language}\label{sec:IL-overview}
\section{Static Language}\label{sec:SL-overview}
\section{Module Language}\label{sec:ML-overview}

>>>>

% !TEX root = omar-thesis.tex
\chapter{Language Overview}\label{chap:language-overview}
\todo{integrate this point}
An important observation is that dialects that have substantially different type structure are still often implemented by translation to a simple and stable intermediate language. For example, the Glasgow Haskell Compiler's intermediate language has remained stable for many years, even as the number of Haskell dialects that the compiler supports has grown. Similarly, the primary Scala compiler uses the Java virtual machine (JVM) bytecode language as an intermediate language, which has also evolved relatively slowly and independently.
\section{External Language}\label{sec:EL-overview}
\section{Internal Language}\label{sec:IL-overview}
\section{Static Language}\label{sec:SL-overview}
\section{Module Language}\label{sec:ML-overview}
